\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{parskip}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}
\title{Comprehensive Feature Test}
\author{LittleTex Test Suite}
\date{\today}
\begin{document}
\maketitle


\section{Level 1 Heading: Document Features}


This is a standard paragraph with some inline formatting. Here is some \textbf{bold text}, some \textit{italic text}, and some \texttt{inline code}.

This is the second line of the same paragraph. The refactored parser should correctly join these lines together.

This is a new paragraph, separated by a single blank line. It demonstrates a simple link to \href{https://code.visualstudio.com/}{the VS Code website}.

This paragraph is separated by multiple blank lines.
It also contains a link with \textbf{bolded text} inside: \href{https://github.com}{\textbf{GitHub}}.

\vspace{0.3cm}
\noindent\hrule
\vspace{0.3cm}

\subsection{Level 2 Heading: Lists and Nesting}


This section tests various list types.

\subsubsection{Level 3 Heading: Bulleted Lists}


\begin{itemize}
\item First item in a bulleted list.
\item Second item, with \textit{italic} and \texttt{code}.
\item A nested list follows:
\begin{itemize}
\item Nested item 1.
\item Nested item 2, which is \textbf{important}.
\begin{itemize}
\item A deeper level of nesting.
\end{itemize}

\end{itemize}

\item Back to the first level.
\end{itemize}


\subsubsection{Level 3 Heading: Numbered Lists}


\begin{enumerate}
\item First item in a numbered list.
\item Second item.
\item A nested numbered list:
\begin{enumerate}
\item Nested item A.
\item Nested item B.
\end{enumerate}

\item Back to the main numbered list.
\end{enumerate}


\vspace{0.3cm}
\noindent\hrule
\vspace{0.3cm}

\subsection{Level 2 Heading: Other Elements}


This is an example of an indented text block, which should be offset from the left margin.

\hspace*{2em}{This text is indented.}

This is a final paragraph to ensure spacing is correct after all other elements.
\end{document}